A formalization of semi-simplicial and semi-cubical sets

### 2023-01-06 paper/paper.tex
paper: beef up bib a bit

\section{Semi-simplicial and semi-cubical sets}
It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices. What we have formalized is \emph{augmented semi-simplicial} sets, and \emph{semi-cubical} sets. We will proceed to explain the mathematical objects we have formalized.

@@

We now present the construction in \emph{extensional} type theory; i.e. in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality:

>>>>

\section{Semi-simplicial and semi-cubical sets}
It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices. What we have formalized is \emph{augmented semi-simplicial} sets~\cite{fri08,riehl11}, and \emph{semi-cubical} sets~\cite{grandis03,buchholtz17}. We will proceed to explain the mathematical objects we have formalized.

@@

We now present the construction in \emph{extensional} type theory; i.e. in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
